```{r, message=FALSE, warning=FALSE}
library(rnoaa)
library(tidyverse)
library(data.table)
```

```{r, message=FALSE}
my_token <- "######" # Token generated using my email (dwfletcher215@tamu.edu)

options(noaakey = my_token) # Sets token allowing interaction with the API

current_date <- Sys.Date()
```

Set up filter conditions. Here, I've filtered on stations that (1) are in Texas and (2) were operational 2010-2020

```{r}
stations <- isd_stations()  # Retrieves full list of ISD stations 

tx_stations <- stations %>% 
  filter(state == "TX") %>% 
  mutate(begin = ymd(begin)) %>% 
  mutate(end = ymd(end))

tx_stations_active <- tx_stations %>%
  filter(year(end) == 2020)  %>% # Check for still being active
  filter(year(begin) <= 2010) # Check for active at the start of timeframe
```

A heuristic check to see if the filtering worked

```{r, fig.asp=.5}
#hist(tx_stations_active$begin, breaks = 75)
```



```{r}
test_data <- isd(usaf = tx_stations_active[10,1], wban = tx_stations_active[10,2], year = 2019)


new_path <- "where you want data to go"

setwd(new_path)
test_data_head <- head(test_data)
save(test_data_head, file="test.Rda")
```


```{r}
#full_data <- data.frame(matrix(0, ncol = length(active_years),nrow = nrow(tx_stations_active)))

full_data <- replicate(n=197, expr=list())
names(full_data) <- tx_stations_active$station_name
```

Creates a vector of important variables to cut down on the size of the data download.

```{r}
imp_vars <- c("date", "time", "latitude", "longitude", "elevation", "wind_direction", "wind_speed", "temperature", "temperature_dewpoint", "air_pressure", "GD1_coverage_code_1", "MA1_station_pressure_rate", "KA1_period_quantity", "KA1_max_min", "KA1_temp", "OC1_speed_rate", "AA1_precipitation_liquid", "AA1_period_quantity_hrs", "AA1_depth", "AU1_intensity_and_proximity_code", "AU1_descriptor_code", "AU1_precipitation_code", "AU1_obscuration_code", "AU1_other_weather_phenomena_code", "AW1_automated_atmospheric_condition_code", "MW1_manual_atmospheric_condition_code")
```

Since the NOAA API needs a specific key per call, this loop cannot be vectorized in a meaningful way. 

```{r}
full_data <- replicate(n=197, expr=list())

for(ii in 1:3){
  iter = 1
  for(jj in 1:length(active_years)){ 
    full_data[[ii]][[iter]] <- 
      data.table(isd(tx_stations_active[ii, 1],
          tx_stations_active[ii, 2],
          year = active_years[jj]))
    
    names(full_data) <- 
      paste(tx_stations_active$station_name[ii], "_", jj)
    
    iter = iter + 1
    }
}
```

########################################################################################################################################################################################################################################

An older version of the assignment that's slower than the one above. 


```{r}
new_path <- "where you want the data to go"
setwd(new_path)

for(ii in 1:197){
  for(jj in 2010:2020){
    outStr <- paste(jj, tx_stations_active$station_name[ii],sep = "_")
    
    assign(outStr, isd(tx_stations_active[ii, 1],
          tx_stations_active[ii, 2],
          year = jj))
    
    saveRDS(outStr, file=paste(outStr, ".Rdata", sep=''))
  }
}


```
